### 2019-11-08 paper/paper.tex
Choices List
Draft of choice list in paper

>>>>

\subsection{Choice Choices} \label{sec:choices}
\begin{itemize}
	\item Using scipy.interpolate.LSQUnivariateSpline to implement cubic spline between lines (fast and incorporates errors well; is chosen spline of the EXPRES pipeline) (and mostly isn't linear)
	\item Interpolating each order individually
	\item Wavelength solutions are delivered on a pixel grid of x and m
	\item Eigenvector determination restricted to orders that are completely covered by LFC lines, and has enough signal to distinguish their peaks (orders 40-75 absolute)
	\item Also restricted to pixels between 500 and 7000 out of 7920 for high signal
	\item Using only exposures from after the replacement of the PCF in July 2019; gave rise to a large change in the nature of the instrument, but still gives us 4 months of data which exhibits non-negligible variation (this may have to be proven?)
	\item Fitting wavelength as dependent variable?  (Should be line centers, right?)
\end{itemize}
